Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere

### 2020-12-28 paper/dcpo_gender_roles.Rmd
add Tai2021

One aspect of latent-variable estimates of public opinion like the PGE dataset that is easy for researchers to overlook is the uncertainty in the estimates.
But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the PGE scores---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2020] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
Therefore, taking the uncertainty in the PGE scores into account is crucial to reaching well-grounded conclusions.

>>>>

One aspect of latent-variable estimates of public opinion like the PGE dataset that is easy for researchers to overlook is the uncertainty in the estimates.
But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the PGE scores---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2021] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
Therefore, taking the uncertainty in the PGE scores into account is crucial to reaching well-grounded conclusions.
